---
title: "20 household_Hourly_aggregated"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### imports
```{r}
library(tidyverse)
library(lubridate)
library(ggplot2)
library(broom)

```

### Read files
```{r}
f <- "aggregated_daily"
files <- list.files(f)



```
### 
```{r}
df_10 <- read_csv(file.path(f, files[1]))
df_11 <- read_csv(file.path(f, files[2]))
df_2 <- read_csv(file.path(f, files[3]))
df_3 <- read_csv(file.path(f, files[4]))
df_4 <- read_csv(file.path(f, files[5]))
df_5 <- read_csv(file.path(f, files[6]))
df_6 <- read_csv(file.path(f, files[7]))
df_7 <- read_csv(file.path(f, files[8]))
df_8 <- read_csv(file.path(f, files[9]))
df_9 <- read_csv(file.path(f, files[10]))
```
### join all the files
```{r}
df_all <- full_join(df_2,df_3, by = "day") %>% 
  full_join(df_4, by = "day" ) %>% 
  full_join(df_5,by = "day") %>% 
  full_join(df_6,by = "day") %>% 
  full_join(df_7,by = "day") %>% 
  full_join(df_8,by = "day") %>% 
  full_join(df_9,by = "day") %>% 
  full_join(df_10,by = "day") %>% 
  full_join(df_11,by = "day") 
```


### renames
```{r}
names(df_all)  <- c('Date',"Aggregate_2", "Aggregate_3","Aggregate_4","Aggregate_5","Aggregate_6",
                      "Aggregate_7", "Aggregate_8","Aggregate_9","Aggregate_10","Aggregate_11")
```

### prepare data for pca(1)
```{r}
df_all <- df_all %>% 
  drop_na() %>% 
  mutate(Date = ymd(Date),
         month  = month(Date),
         day =  day(Date))
```

###Transform: row for each household, column for each day
```{r}

df_longer <- df_all %>% 
  select(-c(month,day)) %>% 
  pivot_longer(Aggregate_2:Aggregate_11, names_to = "Households", values_to = "consumption")

df_wider <- df_longer %>% 
  pivot_wider(names_from = Date, values_from = consumption)

```

###Confirm no columns have 0 variance
```{r}
(map_dbl(df_wider, ~sd(.)) == 0) %>% sum()
```

###Normalise rows

```{r}
for (i in 1:nrow(df_wider)){
  max_value <- max(df_wider[i,-1])
  min_value <- min(df_wider[i,-1])
  df_wider[i,-1] <- (df_wider[i,-1]-min(df_wider[i,-1]))/(max_value - min_value)
}

```
### Calculate the principal components 
```{r}
pcs <- df_wider %>% 
  select(-Households) %>% 
  scale() %>% # standardise the data
  prcomp()
```

# Tidy! 
```{r}
tidy_pcs <- tidy(pcs) ### why??
```
### Scree plot
```{r}
plot(pcs)
```

### Plot first 2 principal components
```{r}
pcs_2 <- tidy_pcs %>%
  filter(PC <= 2) %>% 
  pivot_wider(id_cols = row, 
              names_from = PC)

pcs_2 %>%
  ggplot(aes(x = `1`, y = `2`)) +
  geom_point()
```
### Clustering 2D
```{r}
set.seed(123)

k <- 3

clusters <- tidy_pcs %>%
  filter(PC <= 2) %>% 
  pivot_wider(id_cols = row, 
              names_from = PC) %>%
  select(-row) %>% 
  kmeans(k)

pcs_2_clusters <- pcs_2 %>%
  mutate(cluster = as.factor(clusters$cluster))

pcs_2_clusters %>%
  ggplot(aes(x = `1`, y = `2`, color = cluster)) +
  geom_point()
```
### Elbow plot
```{r}
set.seed(123)

ks <- 2:9
vs <- numeric()
for (k in ks){
  cls <- tidy_pcs %>%
  filter(PC <= 2) %>% 
    pivot_wider(id_cols = row, 
                names_from = PC) %>%
    select(-row) %>% 
    kmeans(k)
    vs <- c(vs, cls$tot.withinss)
}

plot(ks, vs, type = 'b', xlab = 'k', ylab = 'Total within-cluster sum of squares')
```
### Assigning clusters to original customer time series
```{r}
# Add clusters to original time series
df_clusters <- df_wider %>% 
  mutate(cluster = as.factor(clusters$cluster))
view(df_clusters)
rownames(df_clusters) <- as.character(rownames(df_clusters))

# pivot the data
df_clusters_pivot <- df_clusters %>% 
  pivot_longer(`2014-06-03`:`2015-05-10`, names_to = "Date", values_to = "value") 

```

Plot the mean consumption profiles for each cluster

```{r}
mean_power <- df_clusters_pivot %>% 
  group_by(Households,cluster, Date) %>% 
  summarise(mean_power = mean(value),
            upper = quantile(value, 0.75),
            lower = quantile(value, 0.25))
## add facet 
mean_power_1 <- mean_power %>% 
  mutate(Date= ymd(Date),
         Day = wday(Date),
         month = month(Date))
  
```

```{r}
mean_power_1 %>% 
  ggplot(aes(x = Date, 
             y = mean_power, 
             ymin = lower,
             ymax = upper,
             fill = cluster,
             colour = cluster)) + 
  geom_line() + 
  geom_ribbon(alpha = 0.2, color = NA)+
  facet_wrap(~cluster) +
  labs(subtitle = 'Line shows mean power (kW)\nRibbon shows inter-quartile range')
```

